\documentclass{resume}

\usepackage[left=0.40in,top=0.3in,right=0.75in,bottom=0.1in]{geometry}
\usepackage{hyperref}
\usepackage{fontawesome}
\usepackage{lmodern}
\usepackage{setspace}

\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}

\name{Brent Champion}

\address{
	\hfill
	\faLink {\href{https://www.brentchampion.com}{brentchampion.com}}
	\hfill
	\faEnvelope {\href{mailto:brent.champion@queensu.ca}{brent.champion@queensu.ca}}
	\hfill
	\faGithubSquare {\href{https://www.github.com/bchampp}{github.com/bchampp}}
	\hfill
}

\begin{document}

	\begin{rSection}{Education}

		{\bf Queen's University| Kingston, Ontario} \hfill {\em September 2017 - Present} \\
		{\indent \textit{Bachelor of Applied Science in Computer Engineering (Dean's Scholar)}}

	\end{rSection}

	\begin{rSection}{Experience}

		{\bf Queen's AutoDrive} \hfill {\em Kingston, ON} \\
		{\indent \textit{ Integration Lead} \hfill {\em August 2021 - Present}}
		\vspace{-2mm}
		\begin{itemize}
			\setlength{\itemsep}{-8pt}
			\item Leading a team of 50 undergraduate and 7 graduate students to build a Level 4 autonomous vehicle.
			\item Working closely with the perception team to implement novel machine learning techniques.
		\end{itemize}

		{\bf Amazon Web Services} \hfill {\em Vancouver, BC} \\
		{\indent \textit{ Software Engineering Intern} \hfill {\em May 2021 - August 2021}}
		\vspace{-2mm}
		\begin{itemize}
		\setlength{\itemsep}{-8pt}
			\item Developed an internal tool to visualize and manage linking structure across multiple AWS accounts.
			\item Implemented performant graph traversal algorithms to create, update and remove account links.
		\end{itemize}

		{\bf CaseWare International} \hfill {\em Toronto, ON} \\
		{\indent \textit{ Software Engineering Intern} \hfill {\em September 2020 - April 2021}}
		\vspace{-2mm}
		\begin{itemize}
			\setlength{\itemsep}{-8pt}
			\item Worked with Angular, Typescript, Java Spring and AWS to build and maintain an online CRM platform.
			\item Participated in daily standups, code reviews, product design and architecture meetings. 
			\item Contributed to building a highly scalable email service using AWS Lambda.
		\end{itemize}

		{\bf Acoutera} \hfill {\em Vancouver, BC} \\
		{\indent \textit{ Software Engineering Intern} \hfill {\em May 2020 - August 2020}}
		\vspace{-2mm}
		\begin{itemize}
			\setlength{\itemsep}{-8pt}
			\item Participated in weekly sprints using MongoDB, Express, React and Node.js to deliver new features.
			\item Built and hosted a webscraper in Python on AWS to sync the product catalogue on a daily basis.
			\item Pioneered the second iteration of the company platform, using NextJS, ThreeJS and NextAuth. 
		\end{itemize}

		{\bf Robotic Computer Vision Lab (RCV Lab)} \hfill {\em Kingston, ON} \\
		{\indent \textit{ Software Engineering Intern} \hfill {\em May 2019 - April 2020}}
		\vspace{-2mm}
		\begin{itemize}
			\setlength{\itemsep}{-8pt}
			\item Lead on a project to operate and automate data collection with a Gantry Robot in C++.
			\item Built OpenCV programs to improve the quality and efficiency of a 3D data acquisition system.
			\item Worked with a team of graduate students on novel techniques for 3D image processing.
		\end{itemize}

		{\bf Queen's Formula SAE Team} \hfill {\em Kingston, ON} \\
		{\indent \textit{ Electrical Lead} \hfill {\em July 2019 - July 2020}}
		\vspace{-2mm}
		\begin{itemize}
			\setlength{\itemsep}{-8pt}
			\item Led a team of 12 students to design and develop all electrical components for a Formula SAE style car.
			\item Transitioned the powertrain system to a new engine, involving reconfiguring most electrical sub-systems. Improved performance and tuning capabilities by integrating an Electronic Throttle Control system.
		\end{itemize}
		{\indent \textit{ Electrical Team Member} \hfill {\em September 2017 - June 2019}}
		\vspace{-2mm}
		\begin{itemize}
			\setlength{\itemsep}{-8pt}
			\item Designed wiring schematics and PCB layouts. Validated PCBs and sensors for various electrical systems.
			\item Developed an Electronic Throttle Control system, creating new driver assists such as automatic shifting.
		\end{itemize}

	\end{rSection}

	\begin{rSection}{Additional Experience}

		{\bf Queen's Capture the Flag} \hfill {\em November 2020}
		\vspace{-2mm}
		\begin{itemize}
			\setlength{\itemsep}{-8pt}
			\item Competed in a 12-hour security hackathon with two teammates solving diverse cybersecurity challenges.
			\item Placed 1st out of 34 teams by completing the most challenges among the competitors
		\end{itemize}

		{\bf Code Life Ventilator Challenge} \hfill {\em April 2020}
		\vspace{-2mm}
		\begin{itemize}
			\setlength{\itemsep}{-8pt}
			\item Worked in a multidisciplinary team to design, prototype and ship a working ventilator within 2 weeks.
			\item The team placed in the top 9, out of over 1000 submissions spanning 93 countries.
		\end{itemize}

	\end{rSection}

\end{document}